A Survey Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
beefed up related work, tweaked results.

@@

{\color{red} can you comment on the independence, since you have the csv? it would be a pain for me to do find out how many people got the same situational questions which only differ by recipient. :(} There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.

@@

Crowdourcing user studies in Mechanical Turk has its challenges \cite{kittur2008crowdsourcing}. While the Amazon Mechanical Turk population is diverse across several significant demographic dimensions such as age, gender, and income, it is not a precise representation of the U.S. population \cite{ross2010crowdworkers}\cite{kelley2010conducting}. Additionally, Amazon Mechanical Turk workers generally put a higher value on anonymity and hiding information, were more likely to do so, had more privacy concerns than the larger U.S. public \cite{kang2014privacy}.

>>>>

\subsection{Crowdsourced User Studies}
Crowdourcing user studies in Mechanical Turk has its challenges \cite{kittur2008crowdsourcing}. While the Amazon Mechanical Turk population is diverse across several significant demographic dimensions such as age, gender, and income, it is not a precise representation of the U.S. population \cite{ross2010crowdworkers}\cite{kelley2010conducting}. Additionally, Amazon Mechanical Turk workers generally put a higher value on anonymity and hiding information, were more likely to do so, had more privacy concerns than the larger U.S. public \cite{kang2014privacy}.

@@

{\color{red} Serge, this paragraph can be re-worded as you see fit. I just plopped in some stuff.} this test violates that assumption of CHI square, however, based on the condition randomization and very large sample size, we do not believe this to be an issue. Nonetheless, we checked this by also performing the analysis by using only one data point per recipient (to preserve that assumption), and yielded the same results. There might have been a perception of sharing which resulted in sharing with the public being less upsetting than sharing with work contacts--people assumed that sharing it with work was a push and sharing it to the public would require people to pull the available information which was shared.

@@
